\LARGE \bf An Overview of Reinforcement Learning

### 2020-07-15 paper/paper.tex
Add pytorch frameworks and use cases to the code example

\subsection{KerasRL}

keras-rl\cite{plappert2016kerasrl} implements some state-of-the art deep reinforcement learning
algorithms in Python and seamlessly integrates with the deep learning
library Keras.

@@

\subsection{Tensorforce}

Tensorforce~\cite{tensorforce} is an open-source deep reinforcement
learning framework, with an emphasis on modularized flexible library
design and straightforward usability for applications in research and
practice. Tensorforce is built on top of Google's TensorFlow framework
and requires Python 3.

@@

\subsection{Stable Baselines}

Stable Baselines~\cite{stable-baselines}, a set of implementations of
Reinforcement Learning (RL) algorithms with a common interface, based
on OpenAI Baselines. It is focused on simplicity of use and
consistency.

@@

\subsection{TF Agents}

TF-Agents~\cite{TFAgents} is a relatively new but up-and-coming tool, again, from
Google.  TF-Agents, while newer, is typically seen as more robust and
mature. It is a framework designed for notebooks and that makes it
perfect for trying out various configurations, hyperparameters, or
environments.

@@

\addtolength{\textheight}{-9.5cm}   % This command serves to balance the column lengths
% on the last page of the document manually. It shortens
% the textheight of the last page by a suitable amount.
% This command does not take effect until the next page
% so it should come on the page before the last. Make
% sure that you do not shorten the textheight too much.

>>>>

\subsection{TF Agents~\cite{TFAgents}}

TF-Agents is a relatively new but up-and-coming tool, again, from
Google.  TF-Agents, while newer, is typically seen as more robust and
mature. It is a framework designed for notebooks and that makes it
perfect for trying out various configurations, hyperparameters, or
environments.

\subsection{RLlib~\cite{liang2018rllib}}

RLlib is an open-source library for reinforcement learning that offers
both high scalability and a unified API for a variety of
applications. RLlib natively supports TensorFlow, TensorFlow Eager,
and PyTorch, but most of its internals are framework agnostic.

\begin{itemize}
\item  Distributed Prioritized Experience Replay (Ape-X)
\item  Importance Weighted Actor-Learner Architecture (IMPALA)
\item  Asynchronous Proximal Policy Optimization (APPO)
\item  Decentralized Distributed Proximal Policy Optimization (DD-PPO)
\item  Single-Player AlphaZero (contrib/AlphaZero)
\item  Advantage Actor-Critic (A2C, A3C)
\item  Deep Deterministic Policy Gradients (DDPG, TD3)
\item  Deep Q Networks (DQN, Rainbow, Parametric DQN)
\item  Proximal Policy Optimization (PPO)
\item  Soft Actor Critic (SAC)
\item  Augmented Random Search (ARS)
\item  QMIX Monotonic Value Factorisation (QMIX, VDN, IQN)
\item  Multi-Agent Deep Deterministic Policy Gradient (contrib/MADDPG)
\item  Advantage Re-Weighted Imitation Learning (MARWIL)
\item  Linear Upper Confidence Bound (contrib/LinUCB)
\item  Linear Thompson Sampling (contrib/LinTS)
\end{itemize}

\subsection{SLM Lab~\cite{kenggraesser2017slmlab}}

SLM Lab is a software framework for reproducible reinforcement
learning research. It enables easy development of RL algorithms using
modular components and file-based configuration. It also enables
flexible experimentation completed with hyperparameter search, result
analysis and benchmark results.

\begin{itemize}
\item SARSA
\item DQN (Deep Q-Network)
\item Double-DQN, Dueling-DQN, PER (Prioritized Experience Replay)
\item REINFORCE
\item A2C (Advantage Actor-Critic) with GAE \& n-step
\item PPO (Proximal Policy Optimization)
\item SAC (Soft Actor-Critic)
\item SIL (Self Imitation Learning)
\end{itemize}

\subsection{KerasRL~\cite{plappert2016kerasrl}}

keras-rl implements some state-of-the art deep reinforcement learning
algorithms in Python and seamlessly integrates with the deep learning
library Keras.

@@

\subsection{Tensorforce~\cite{tensorforce}}

Tensorforce is an open-source deep reinforcement
learning framework, with an emphasis on modularized flexible library
design and straightforward usability for applications in research and
practice. Tensorforce is built on top of Google's TensorFlow framework
and requires Python 3.

@@

\subsection{Stable Baselines~\cite{stable-baselines}}

Stable Baselines, a set of implementations of
Reinforcement Learning (RL) algorithms with a common interface, based
on OpenAI Baselines. It is focused on simplicity of use and
consistency.

@@

@@

\addtolength{\textheight}{-17cm}   % This command serves to balance the column lengths
% on the last page of the document manually. It shortens
% the textheight of the last page by a suitable amount.
% This command does not take effect until the next page
% so it should come on the page before the last. Make
% sure that you do not shorten the textheight too much.
